Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2019-12-22 analysis/paper/paper.Rmd
minor updates

# The progressive capture of shape geometry along the number of harmonics can be visualized with:
calibrate_reconstructions_efourier(jpgs_imported_coo,  
                          id = 1, 
                          range = c(1, 2, 4, 8, 14, 20))

@@

The elliptic Fourier coefficients of `r total_no` pottery from three different phases were calculated. Reliable pottery outline was captured by 13 harmonics that gather 99 % of the total harmonic power. Thin-plate splines compares the average shapes of vessels from each period to visualize the outline deformations required to pass from an extreme of one morphospace to the other.

@@

Outlines generated by EFA are examined by principal components analysis to explore the shape variations across three phases. The first two principal components (PCs) explain `r vari_two`% of variances, and the first three principal components (PCs) explain `r vari_three`% of variances. The PC1 relate to the height of the vessels from short to high, the PC2 reflects the width of their necks and mouths from narrow to wide, and the PC3 relates to the degree of flare of neck from curve to straight. The biplot of PCs presents the grouping by each occupation phase.

>>>>

@@

The elliptic Fourier coefficients of `r total_no` pottery from three different phases were calculated. Reliable pottery outline was captured by 13 harmonics that gather 99 % of the total harmonic power. Thin-plate splines compares the average shapes of vessels from each period to visualize the outline deformations required to pass from an extreme of one morphospace to the other. The

@@

Outlines generated by EFA are examined by principal components analysis to explore the shape variations across three phases. The first two principal components (PCs) explain `r vari_two`% of variances, and the first three principal components (PCs) explain `r vari_three`% of variances. The PC1 relate to the height of the vessels from short to high, the PC2 reflects the neck and mouth constriction from wide to narrow, and the PC3 relates to the degree of flare of neck from curved to straight shape. The biplot of PCs presents the grouping by each occupation phase.
